SeedLing: Building and using a seed corpus \\ for the Human Language Project

### 2014-05-20 docs/computEL-final/intro.tex
Small typo

To produce SeedLing, we have drawn on four web sources, described in section \ref{sec:sources}. To bring the four resources into a single common format and data structure (section \ref{sec:structure}), each required different degrees and types of cleaning and standardisation. We describe the steps required in section \ref{sec:case_studies}, presenting each resource as a separate mini-case study. We hope that the lessons we learned in assembling our seed corpus can guide future resource conversion efforts. To that end, many of the resources described in section~\ref{sec:related} are candidates for inclusion in the next stage of building a Universal Corpus.

>>>>

To produce SeedLing, we have drawn on four web sources, described in section \ref{sec:sources}. To bring the four resources into a common format and data structure (section \ref{sec:structure}), each required different degrees and types of cleaning and standardisation. We describe the steps required in section \ref{sec:case_studies}, presenting each resource as a separate mini-case study. We hope that the lessons we learned in assembling our seed corpus can guide future resource conversion efforts. To that end, many of the resources described in section~\ref{sec:related} are candidates for inclusion in the next stage of building a Universal Corpus.
